---
title: "p8105_hw1_mk4996"
author: "Miho Kawanami"
date: "2025-09-19"
output: github_document
---

### Problem 1
```{r setup, include=FALSE}
library(moderndive)
data("early_january_weather")
```

The dataset `early_january_weather` contains hourly meteorological data for LGA, JFK and EWR in early January 2013.  
It has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
The important variables include:

- **time_hour**: time of measurement  
- **temp, dewp**: temperature and dewpoint in Fahrenheit  
- **humid**: relative humidity  
- **wind_dir, wind_speed, wind_gust**: wind direction (in degrees), speed and gust speed (in mph)

The mean temperature during this period was `r mean(early_january_weather$temp, na.rm = TRUE)` °F.

### Scatterplot of temperature vs. time
```{r scatterplot, message=FALSE, warning=FALSE}
library(tidyverse)

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs Time in Early January (NYC airports)",
    x = "Time (hour)",
    y = "Temperature (°F)",
    color = "Humidity (%)"
  )
```


