---
title: "p8105_hw1_mk4996"
author: "Miho Kawanami"
date: "2025-09-19"
output: github_document
---

## Problem 1
```{r setup, include=FALSE}
library(moderndive)
data("early_january_weather")
```

The dataset `early_january_weather` contains hourly meteorological data for LGA, JFK and EWR in early January 2013.  
It has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
The important variables include:

- **time_hour**: time of measurement  
- **temp, dewp**: temperature and dewpoint in Fahrenheit  
- **humid**: relative humidity  
- **wind_dir, wind_speed, wind_gust**: wind direction (in degrees), speed and gust speed (in mph)

The mean temperature during this period was `r mean(early_january_weather$temp, na.rm = TRUE)` °F.

### Scatterplot of temperature vs. time
```{r scatterplot, message=FALSE, warning=FALSE}
library(tidyverse)

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs Time in Early January (NYC airports)",
    x = "Time (date and hour)",
    y = "Temperature (°F)",
    color = "Humidity (%)"
  )
ggsave("scatterplot.pdf",  ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
         geom_point())
```
Overall, the temperature gradually increased until around January 14, after which it dropped sharply. Humidity levels were highest around January 12–13, as shown by the lighter blue points in the plot. This suggests that the warmest period overlapped with the peak in humidity.

## Problem 2
### data frame
```{r}
set.seed(1234)

p2_df=tibble(
  x_num = rnorm(10, mean = 0, sd = 1),
  x_logical = x_num > 0,
  x_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  x_fac = factor(sample(c("low","mid","high"), 10, replace = TRUE),
          levels = c("low","mid","high"))
)
```

### mean
```{r}
library(tidyverse)

mean(pull(p2_df, x_num))
mean(pull(p2_df, x_logical))   
mean(pull(p2_df, x_char))
mean(pull(p2_df, x_fac))
```
The means of the random sample and logical variables could be calculated, but the means of the character and factor variables could not.

### as.numeric
```{r, results='hide', warning=FALSE}
as.numeric(pull(p2_df, x_logical)) 
as.numeric(pull(p2_df, x_char))
as.numeric(pull(p2_df, x_fac))  

``` 
Based on the as.numeric results, logical values are converted to 0/1, character values are treated as NA, and factors are converted to the numbers assigned to each level. Consequently, the means of the numeric and logical variables can be computed, whereas the means of the character and factor variables cannot be calculated directly because they are not numeric or meaningful. 