---
title: "p8105_hw1_mk4996"
author: "Miho Kawanami"
date: "2025-09-19"
output: github_document
---

### Problem 1
```{r setup, include=FALSE}
library(moderndive)
data("early_january_weather")
```

The dataset `early_january_weather` contains hourly meteorological data for LGA, JFK and EWR in early January 2013.  
It has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
The important variables include:

- **time_hour**: time of measurement  
- **temp, dewp**: temperature and dewpoint in Fahrenheit  
- **humid**: relative humidity  
- **wind_dir, wind_speed, wind_gust**: wind direction (in degrees), speed and gust speed (in mph)

The mean temperature during this period was `r mean(early_january_weather$temp, na.rm = TRUE)` °F.

### Scatterplot of temperature vs. time
```{r scatterplot, message=FALSE, warning=FALSE}
library(tidyverse)

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs Time in Early January (NYC airports)",
    x = "Time (hour)",
    y = "Temperature (°F)",
    color = "Humidity (%)"
  )
ggsave("scatterplot.pdf",  ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
         geom_point())
```


### Problem 2
```{r}
p2_df=tibble(
x_num = rnorm(10, mean = 0, sd = 1),
x_logical = x_num > 0,
x_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
x_fac = factor(sample(c("low","mid","high"), 10, replace = TRUE),
        levels = c("low","mid","high"))
)

library(tidyverse)

mean(pull(p2_df, x_num))
mean(pull(p2_df, x_logical))   
mean(pull(p2_df, x_char))
mean(pull(p2_df, x_fac))
# Error: 'mean' not meaningful for character, 'mean' not meaningful for factors
```

```{r}
mean(as.numeric(pull(p2_df, x_fac)))   
mean(as.numeric(pull(p2_df, x_char)))  
```
